Measurement and Analysis of Child Pornography Trafficking on P2P Networks\nocite{Hurley}

### 2013-10-15 Paper_presentation.tex
Corrigido .

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.5]{FOI_redundancy}
\caption{Count of how many IDs are sharing the same file}.
\label{fig:FOI_redundancy}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.5]{FOI_availability}
\caption{Count of days a file has been found online}.
\label{fig:FOI_availability}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.35]{CDF_characterization_gnutella}
\caption{Cumulative distribution function (Gnutella)}.
\label{fig:CDF_characterization_gnutella}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.35]{CDF_characterization_emule}
\caption{Cumulative distribution function (eMule)}.
\label{fig:CDF_characterization_emule}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.3]{Libraries_specific_day}
\caption{Gnutella unique libraries on specific days}.
\label{fig:Libraries_specific_day}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.25]{Libraries_unique}
\caption{Uniquesses of partial and complete libraries using Jaccard index}.
\label{fig:Libraries_unique}
\end{figure}

>>>>

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.5]{FOI_redundancy}
\caption{Count of how many IDs are sharing the same file}
\label{fig:FOI_redundancy}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.5]{FOI_availability}
\caption{Count of days a file has been found online}
\label{fig:FOI_availability}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.35]{CDF_characterization_gnutella}
\caption{Cumulative distribution function (Gnutella)}
\label{fig:CDF_characterization_gnutella}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.35]{CDF_characterization_emule}
\caption{Cumulative distribution function (eMule)}
\label{fig:CDF_characterization_emule}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.3]{Libraries_specific_day}
\caption{Gnutella unique libraries on specific days}
\label{fig:Libraries_specific_day}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.25]{Libraries_unique}
\caption{Uniquesses of partial and complete libraries using Jaccard index}
\label{fig:Libraries_unique}
\end{figure}
